\vspace{-2cm} The effects of transitions of power on the contents of municipal government websites

### 2017-12-06 paper/manuscript.tex
finally managed to get the cross city entropy for different duplicate lines removal cutoffs to work
cutoffs entropy with topic weights + improvements to clusters more plots, etc.

@@

>>>>

%Heatmaps with no duplicate line removal (threshold set at 999999999)
%also, since the duplicate line removal didn't get rid of as much crap,
%it was necessary to remove non [A-Za-z] characters before hunspell
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Word-topic probabilities for topics with big partisan differences, across documents (Indiana). No duplicate line removal.}
	\label{heatmaps_weights}
	\includegraphics[width=\linewidth]{figures/heatmaps_weights_noDuplicateRemoval_IN.png}
\end{figure}

@@

%Entropy by cutoff
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Entropy (between cities, for each topic).}
	\label{cutoffEntropy}
	\includegraphics[width=\linewidth]{figures/CutoffCityEntropy.pdf}
\end{figure}

%Weighted entropy by cutoff
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Weighted (multiplied by tokens assigned to the topic) entropy (between cities, for each topic).}
	\label{cutoffEntropy}
	\includegraphics[width=\linewidth]{figures/CutoffCityEntropyWeighted.pdf}
\end{figure}

%Clustering
\begin{figure}[!ht]
	\centering
	\caption{Log number of city documents per cluster. Brighter tile colors indicate more documents. The color of the tile border indicates the city's party.}
	\label{hclustCity10}
	\includegraphics[width=\linewidth]{figures/heatmap_hclust_10.png}
\end{figure}

%Clustering
\begin{figure}[!ht]
	\centering
	\caption{Log number of city documents per cluster. Brighter tile colors indicate more documents. The color of the tile border indicates the city's party.}
	\label{hclustCity20}
	\includegraphics[width=\linewidth]{figures/heatmap_hclust_20.png}
\end{figure}

%Clustering
\begin{figure}[!ht]
	\centering
	\caption{Log number of city documents per cluster. Brighter tile colors indicate more documents. The color of the tile border indicates the city's party.}
	\label{hclustCity30}
	\includegraphics[width=\linewidth]{figures/heatmap_hclust_30.png}
\end{figure}

%Clustering
\begin{figure}[!ht]
	\centering
	\caption{Log number of city documents per cluster. Brighter tile colors indicate more documents. The color of the tile border indicates the city's party.}
	\label{hclustCity40}
	\includegraphics[width=\linewidth]{figures/heatmap_hclust_40.png}
\end{figure}

%Clustering
\begin{figure}[!ht]
	\centering
	\caption{Log number of city documents per cluster. Brighter tile colors indicate more documents. The color of the tile border indicates the city's party.}
	\label{hclustCity50}
	\includegraphics[width=\linewidth]{figures/heatmap_hclust_50.png}
\end{figure}

%Clustering
\begin{figure}[!ht]
	\centering
	\caption{Log number of city documents per cluster. Brighter tile colors indicate more documents. The color of the tile border indicates the city's party.}
	\label{hclustCity100}
	\includegraphics[height = 1.2\textheight]{figures/heatmap_hclust_100.png}
\end{figure}
